---
title: "DataGenerator"
author: "Anonymous"
output: html_document
---

# Instructions
To run the DataGenerator.Rmd file, follow the following steps:

Step 1: Ensure that you are in the correct working directory
Step 2: Set the Seed you would like to use
Step 3: Run the Generator



# Step 1
First ensure that the working directory of this program leads to the file "../Table_4" on your machine.
```{r}
getwd()
#setwd()
```

# Step 2
Then simply set the seed you would like to use then run the following cells. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(ggplot2)
pi = 3.14159
set.seed(23456)
```

# Step 3

```{r}
library(plotly)


f = function(x){
  # x = (x+0.2)/(1.4)
  r = sum((x-0.5)^2)
  y = (1/(1+3*r) + 2*r)
  return(0.2*sin(40*r))
}
f = function(x){
  # x = (x+0.2)/(1.4)
  r = sum((x-0.5)^2)
  return(0.2*sin(100*r))
}



N = 234
#N = 100

grid1 = expand.grid(seq(0.2,0.8,length.out = N),seq(0.2,0.8,length.out = N)) %>% as.matrix()
grid2 = expand.grid(seq(0.25,0.251,length.out = N),seq(0.25,0.251,length.out = N)) %>% as.matrix()
grid = rbind(grid1,grid2)


#grid[,1]

z = apply(grid,1,f)
x = grid

df = data.frame(x = x[,1],y=x[,2],z=z)

p <- plot_ly(
    df, x= ~x, y= ~y, z= ~z,
    type='mesh3d', intensity = ~z,
    colors= colorRamp(rainbow(5))
  )
#p


s2 = 5*10^(-0)
s2 = 0.1*10^(-0)

y = x %>% apply(1,f)
y_true = y
y = rnorm(nrow(grid),y,sd = sqrt(s2))

#mean((y-y_true)^2)

data = data.frame(x1 = grid[,1], x2 = grid[,2], y = y, y_true = y_true)
training0 = sample(nrow(grid), 80000)
#training0 = sample(nrow(grid), 10000)
#training0 %>% length()
data$training = 0
data[training0,]$training = 1
save(data, file = "data_2d_dense.RData")



load("data_2d_dense.RData")
data %>% str()
write.csv(data,"data_2d_dense.csv")


data %>% names()

train_x = data[data$training == 1,c(1,2)]
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,c(1,2)]
test_y = data[data$training == 0,]$y

write.table(train_x,"train_x_2d_dense.csv", row.names = F, col.names = F)
write.table(train_y,"train_y_2d_dense.csv", row.names = F, col.names = F)


write.table(test_x,"test_x_2d_dense.csv", row.names = F, col.names = F)
write.table(test_y,"test_y_2d_dense.csv", row.names = F, col.names = F)

```
