---
title: "HS-SVD"
author: "Anonymous"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pracma)
library(Rlinsolve)
library(profmem)
library(peakRAM)
library(plotly)
library(cPCG)
library(microbenchmark)
library(Matrix)



logdet = function(A){
  return(unname(unlist(determinant(A,logarithm=T)))[1])
}


```



### HS-SVD method
This cell defines the HS-SVD method. The method takes in parameters:
  x     - a set of predictors
  y     - a set of outcomes
  x_new - a set of new predictor values at which to make new predictions
  init  - initial guess for the parameter values
  beta  - smoothness parameter
```{r}
phifunc = function(n,x){
  return(sqrt(2)*sin(pi*x*n))
}

hssvd_predict = function(x,y,x_new, init,M, beta = 1){
  N = length(x)
  Phi = sqrt(2)*sin(pi* x %*% t(c(1:M)))
  phi_T_phi = t(Phi) %*% Phi
  phi_T_y = t(Phi) %*% y
  sum_y2 = t(y) %*% y
  
  nlik = function(h_param,n, beta,Y, verbose = 1, Phi, phi_T_phi){
    if(verbose == 1){cat("-")}
    eps = exp(h_param[1])
    s2  = exp(h_param[2])
    rho = exp(h_param[3])
    Lambda = rho*(((1:M)*pi)^2+eps^2)^(-beta)

    t1 <- sum_y2 - t(cgsolve(s2 * diag(1/Lambda) + phi_T_phi, phi_T_y)) %*% phi_T_y
    t1 <- t1/s2
    t2 <- (n-M)*log(s2) + log(det( s2*diag(1,M) + phi_T_phi %*% diag(Lambda)   ))
    return(t1 + t2)
  }
  
  
  out = optim(init,nlik, method = "Nelder-Mead", n = N, beta = beta, Y=y, verbose = 1, Phi = Phi, phi_T_phi = phi_T_phi)$par
  print(out)

  eps = exp(out[1])
  s2  = exp(out[2])
  rho = exp(out[3])
  
  Lambda = rho*(((1:M)*pi)^2+eps^2)^(-beta)
  K_inv_y = (1/s2) * (y - Phi %*% cgsolve(  s2*diag(1/Lambda) + phi_T_phi  ,  phi_T_y   ))
  y_new = t(outer(1:M,x_new,phifunc)) %*% (diag(Lambda) %*% (t(Phi) %*% K_inv_y))

  return(y_new)
}

```


### Carrying out the simulation
This cell imports the data and processes it

```{r data prep}
load("data_1D_100k.RData")

data_train = data %>% filter(training == 1)
data_train %>% str()
data_test = data %>% filter(training == 0)
```
This cell performs the simulations. The initial value for $\rho$ must be approximately $3\epsilon$, and the initial value for $\epsilon$ should be between 6 and 14. Otherwise numerical instability will occur.
```{r}
N = nrow(data)
M = 50
beta = 3



result <- peakRAM({
  hssvd_predict(data_train$x,data_train$y,data_test$x,c(8,-2,30),M, beta = beta)
})

eps_0 = 6
plot(hssvd_predict(data_train$x,data_train$y,data_test$x,c(eps_0,2,eps_0*3),M, beta = beta))

result


mse_l  = c()
time_l = c()

for(i in c(1:10)){
  mytime = system.time(yhat <- hssvd_predict(data_train$x,data_train$y,data_test$x,c(8,-2,30),M, beta = beta))
  time_l = c(time_l,mytime[3] %>% unname())
  mse_l = c(mse_l,mean((yhat - data_test$y)^2))
}

mse_l %>% mean()
mse_l %>% sd()

time_l %>% mean()
time_l %>% sd()
```


This cell prints out the results. The standard deviations are in paratheses, i.e. Mean (SD)
```{r}
cat(
  "Mean MSE:",
  mse_l %>% mean(),
  "(",mse_l %>% sd(),")",

  "Mean Time:",
  time_l %>% mean(),
  "(",time_l %>% sd(),")"
)

```
