---
title: "DataGenerator"
author: "Anonymous"
output: html_document
---





# Instructions
To run the DataGenerator.Rmd file, follow the following steps:

Step 1: Ensure that you are in the correct working directory
Step 2: Set the Seed you would like to use
Step 3: Run the Generator



# Step 1
First ensure that the working directory of this program leads to the file "../Table_2" on your machine.
```{r}
getwd()
#setwd()
```


# Step 2
Then simply set the seed you would like to use then run the following cells. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(ggplot2)
pi = 3.14159

# Set the seed you will use for your simulations
set.seed(23456)
```




# Step 3

```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  
N = 100000


x = c(seq(0.2,0.8,length.out = N/2),seq(0.25,0.251,length.out = N/2))

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)



save(data, file = "data_1D_100k_Dense.RData")

plot(y~x)
lines(y_true~x, col = "red")

```


```{r}

load("data_1D_100k_Dense.RData")
data
write.csv(data,"data_1D_100k_Dense_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"train_x_100k_Dense.csv", row.names = F, col.names = F)
write.table(train_y,"train_y_100k_Dense.csv", row.names = F, col.names = F)


write.table(test_x,"test_x_100k_Dense.csv", row.names = F, col.names = F)
write.table(test_y,"test_y_100k_Dense.csv", row.names = F, col.names = F)

```
