---
title: "HS-SVD"
author: "Anonymous"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pracma)
library(Rlinsolve)
library(profmem)
library(peakRAM)
library(plotly)
library(cPCG)
library(microbenchmark)
library(Matrix)


logdet = function(A){
  return(unname(unlist(determinant(A,logarithm=T)))[1])
}
```

### Carrying out the simulation
This cell imports the data and processes it

```{r data prep}
load("data_2d.RData")
#load("data_2d_dense.RData")
data %>% str()

data

data_train = data %>% filter(training == 1)
data_test = data %>% filter(training == 0)

str(data_train)

str(data_test)

df = data.frame(x = data$x1,y=data$x2,z=data$y)
p <- plot_ly(
    df, x= ~x, y= ~y, z= ~z,
    type='mesh3d', intensity = ~z,
    colors= colorRamp(rainbow(5))
  )
#p



```


### HS-SVD method
This cell defines the HS-SVD method. The method takes in parameters:
  x     - a set of predictors
  y     - a set of outcomes
  x_new - a set of new predictor values at which to make new predictions
  init  - initial guess for the parameter values
  beta  - smoothness parameter

```{r}
phifunc = function(m,x){
  indices = expand.grid(1:m,1:m)
  phi = matrix(0, nrow = ((m)^2), ncol = nrow(x))
  for(i in 1:nrow(indices)){
    phi[i,] = sin(indices[i,1] * pi * x[,1])*sin(indices[i,2] * pi * x[,2])
  }
  return(phi)
}



lambdafunc = function(m,eps,beta){
  indices = expand.grid(1:m,1:m)
  lambda = 0*(1:nrow(indices))
  i_2 = indices^2
  i_2 = i_2[,1] + i_2[,2]
  lambda = ((pi^2)*(i_2) + eps^2)^(-beta)
  return(lambda)
}



hssvd_predict_2d = function(x,y,x_new, init = c(0,0,0),M, beta = 1){
  #browser()
  N = nrow(x)
  Phi = phifunc(M,x) %>% t()
  phi_T_phi = t(Phi) %*% Phi
  print(Phi %>% dim())
  #cat("y: ", y)
  phi_T_y = t(Phi) %*% y %>% as.matrix()
  sum_y2 = t(y) %*% y
  MM = nrow(phi_T_phi)
  
  
  nlik = function(h_param,n, beta,Y, verbose = 1, Phi, phi_T_phi){
    #time = Sys.time()
    #browser()
    if(verbose == 1){cat("-")}
    eps = exp(h_param[1])
    s2  = exp(h_param[2])
    rho = exp(h_param[3])
    #print(h_param)
    Lambda = lambdafunc(M, eps, beta)*rho
    
    
    t1 <- sum_y2 - t(cgsolve(s2 * diag(1/Lambda) + phi_T_phi, phi_T_y)) %*% phi_T_y
    #t1 <- t(Y) %*% Y - t(Y) %*% Phi %*% cgsolve(s2 * diag(1/Lambda) + phi_T_phi, phi_T_y)
    t1 <- t1/s2
    t2 <- (n-M)*log(s2) + log(det( s2*diag(1,MM) + phi_T_phi %*% diag(Lambda)   ))
    # print(t1)
    # print(t2)
    return(t1 + t2)
  }
  
  # 
  # #"Nelder-Mead"
  # #"BFGS"
  out = optim(init,nlik, method = "Nelder-Mead", n = N, beta = beta, Y=y, verbose = 1, Phi = Phi, phi_T_phi = phi_T_phi,control = list(reltol = 1e-8))$par
  print(out)
  #cat("eps, s2:",exp(out))
  #init = c(5,-40)
  eps = exp(out[1])#exp(out[1])
  s2  = exp(out[2])#exp(out[2])
  rho = exp(out[3])
  Lambda = lambdafunc(M, eps, beta)*rho
  # Hy = (y/s2) - (1/(s2))*Phi %*% (cgsolve((s2*diag(1/Lambda) + phi_T_phi), (phi_T_y), tol = 1e-16))
  # y_new = t(phifunc(M,x_new)) %*% (Lambda * (t(Phi) %*% Hy))
  
  K_inv_y = (1/s2) * (y - Phi %*% cgsolve(  s2*diag(1/Lambda) + phi_T_phi  ,  phi_T_y  , tol = 1e-16 ))
  y_new = t(phifunc(M,x_new)) %*% (diag(Lambda) %*% (t(Phi) %*% K_inv_y))
  return(y_new)
}



#y_new = hssvd_predict_2d(data_train[,c(1,2)],data_train$y,data_test[,1:2],init,13,4)

#system.time(y_new <- hssvd_predict_2d(data_train[,c(1,2)],data_train$y,data_test[,1:2],init,13,4))

# result <- profmem({
#   hssvd_predict_2d(data_train[,c(1,2)],data_train$y,data_test[,1:2],init,13,4)
# })
# 
# print(result$bytes %>% sum() / (1024^2))

```


This cell performs the simulations
```{r}
M = 13

data_train %>% str()

result <- peakRAM({
    y_new <- hssvd_predict_2d(data_train[,c(1,2)],data_train$y,data_test[,1:2],c(5,-4,30),M ,beta = 4)
})


print(result)

mean((data_test$y-y_new)^2) %>% print()
```


```{r}
M = 13

mse_l = c()
time_l = c()



for(i in c(1:10)){  

  result <- system.time({
    y_new <- hssvd_predict_2d(data_train[,c(1,2)],data_train$y,data_test[,1:2],c(5,-4,30),M,4)
  })  
  
  time_l = c(time_l,result[3] %>% unname())
  mse_l = c(mse_l,mean((y_new - data_test$y)^2))
  print(result)

}

mean((y_new - data_test$y)^2)

mse_l %>% mean()
mse_l %>% sd()

time_l %>% mean()
time_l %>% sd()

```

This cell prints out the results. The standard deviations are in paratheses, i.e. Mean (SD)
```{r}
cat(
  "Mean MSE:",
  mse_l %>% mean(),
  "(",mse_l %>% sd(),")",

  "Mean Time:",
  time_l %>% mean(),
  "(",time_l %>% sd(),")"
)

```



