---
title: "DataGenerator"
author: "Anonymous"
output: html_document
---

# Instructions
To run the DataGenerator.Rmd file, follow the following steps:

Step 1: Ensure that you are in the correct working directory
Step 2: Set the Seed you would like to use
Step 3: Run the Generator



# Step 1
First ensure that the working directory of this program leads to the file "../Table_4" on your machine.
```{r}
getwd()
#setwd()
```

# Step 2
Then simply set the seed you would like to use then run the following cells. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(ggplot2)
pi = 3.14159
set.seed(23456)
```


# Step 3

```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 2000


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_2k.RData")
plot(y~x)
lines(y_true~x, col = "red")


ggplot()+
  geom_line(aes(y = y_true, x = x))+
  labs(
    #title = "True Function in Simulations 1 and 2",
    #subtitle = "Data from the mpg dataset",
    x = "X", # X-axis label
    y = "Y"#,     # Y-axis label
    #caption = "Source: ggplot2 mpg dataset"
  )+
  theme(
    #plot.title = element_text(size = 20, face = "bold"),    # Title size
    #plot.subtitle = element_text(size = 16),               # Subtitle size
    axis.title.x = element_text(size = 20),                # X-axis label size
    axis.title.y = element_text(size = 20),                # Y-axis label size
    axis.text.x = element_text(size = 12),                 # X-axis tick label size
    axis.text.y = element_text(size = 12),                 # Y-axis tick label size
    #plot.caption = element_text(size = 10)                 # Caption size
  )


load("Data/data_1D_2k.RData")
data
write.csv(data,"Data/data_1D_2k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_2k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_2k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_2k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_2k.csv", row.names = F, col.names = F)
```
```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 20000


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_20k.RData")
plot(y~x)
lines(y_true~x, col = "red")


load("Data/data_1D_20k.RData")
data
write.csv(data,"Data/data_1D_20k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_20k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_20k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_20k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_20k.csv", row.names = F, col.names = F)
```

```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 31697


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_31k.RData")
plot(y~x)
lines(y_true~x, col = "red")


load("Data/data_1D_31k.RData")
data
write.csv(data,"Data/data_1D_31k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_31k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_31k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_31k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_31k.csv", row.names = F, col.names = F)
```


```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 50237


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_50k.RData")
plot(y~x)
lines(y_true~x, col = "red")


load("Data/data_1D_50k.RData")
data
write.csv(data,"Data/data_1D_50k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_50k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_50k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_50k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_50k.csv", row.names = F, col.names = F)
```


```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 79621


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_80k.RData")
plot(y~x)
lines(y_true~x, col = "red")


load("Data/data_1D_80k.RData")
data
write.csv(data,"Data/data_1D_80k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_80k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_80k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_80k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_80k.csv", row.names = F, col.names = F)
```



```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 126191


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

#scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
#scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_120k.RData")
plot(y~x)
lines(y_true~x, col = "red")


load("Data/data_1D_120k.RData")
data
write.csv(data,"Data/data_1D_120k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_120k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_120k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_120k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_120k.csv", row.names = F, col.names = F)
```



```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  

N = 200000


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)




save(data, file = "Data/data_1D_200k.RData")
plot(y~x)
lines(y_true~x, col = "red")

load("Data/data_1D_200k.RData")
data
write.csv(data,"Data/data_1D_200k_csv.csv")


train_x = data[data$training == 1,]$x
train_y = data[data$training == 1,]$y

test_x = data[data$training == 0,]$x
test_y = data[data$training == 0,]$y

write.table(train_x,"Data/train_x_200k.csv", row.names = F, col.names = F)
write.table(train_y,"Data/train_y_200k.csv", row.names = F, col.names = F)


write.table(test_x,"Data/test_x_200k.csv", row.names = F, col.names = F)
write.table(test_y,"Data/test_y_200k.csv", row.names = F, col.names = F)
```


## Generator for 2M data

```{r}
f = function(x){
  # x = (x+0.2)/(1.4)
  return(sin(300*(x-0.5)^2))
}
  
N = 2*10^(6)


x = seq(0.2,0.8,length.out = N)

s2 = 5*10^(-0)
s2 = 0.3*10^(-0)

y = x %>% sapply(f)
y = y-mean(y)
y = y/(sd(y))
y_true = y
y = rnorm(N,y,sd = sqrt(s2))


data = data.frame(x = x, y = y, y_true = y_true)
training0 = sample(N, floor(0.8*N))
training0 %>% length()
data$training = 0
data[training0,]$training = 1

str(data)

# #scatter.smooth(data$x,data$training, span = 2/3, degree = 0, family =)
# #scatter.smooth(data$x,data$y_true)


save(data, file = "Data/data_1D_2M.RData")

# plot(y~x)
# lines(y_true~x, col = "red")

```








